---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r}
#| include = FALSE

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# cleanventory

<!-- badges: start -->
[![R-CMD-check](https://github.com/RaoulWolf/cleanventory/workflows/R-CMD-check/badge.svg)](https://github.com/RaoulWolf/cleanventory/actions)
[![Codecov test coverage](https://codecov.io/gh/RaoulWolf/cleanventory/branch/master/graph/badge.svg)](https://app.codecov.io/gh/RaoulWolf/cleanventory?branch=master)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

The goal of cleanventory is to provide easy access to cleaned and partially 
curated data sets of common chemical inventories. 

As of `r Sys.Date()`, the following inventories are included: 


| Chemical Inventory | Name   | Version   | URL                                                                |
|:------------------ |:------ |:--------- |:------------------------------------------------------------------ |
| US EPA TSCA        | `tsca` | 2021-08   | https://www.epa.gov/tsca-inventory                                 |
| ECHA CLP Annex VI  | `clp`  | 17        | https://echa.europa.eu/en/information-on-chemicals/annex-vi-to-clp |
| ECHA EC            | `ec`   | *Unknown* | https://echa.europa.eu/information-on-chemicals/ec-inventory       |


## Installation

You can install the development version of cleanventory from 
[GitHub](https://github.com/) with:

```{r install}
#| eval = FALSE

# install.packages("devtools")
remotes::install_github("RaoulWolf/cleanventory")
```

## Examples

This is an example which shows you how to get the data set of the US EPA TSCA:

```{r example}
library(cleanventory)
str(tsca)
```
