---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r}
#| include = FALSE

knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# cleanventory <img src="man/figures/logo.svg" align="right" height="139" />

<!-- badges: start -->
[![R-CMD-check](https://github.com/RaoulWolf/cleanventory/workflows/R-CMD-check/badge.svg)](https://github.com/RaoulWolf/cleanventory/actions)
[![Codecov test coverage](https://codecov.io/gh/RaoulWolf/cleanventory/branch/master/graph/badge.svg)](https://app.codecov.io/gh/RaoulWolf/cleanventory?branch=master)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->

> A [ZeroPM](https://zeropm.eu/) R package

The goal of cleanventory is to provide easy access to cleaned and partially 
curated data sets of common chemical inventories. In addition to the cleaned
inventories, cleanventory also provides the functions to clean up the original
files of the inventories. 

As of `r Sys.Date()`, the following inventories are included: 

| Chemical Inventory | Name   | Function       | Version(s)            | URL                                                                |
|:------------------ |:------ |:-------------- |:--------------------- |:------------------------------------------------------------------ |
| US EPA TSCA        | `tsca` | `clean_tsca()` | 2021-08               | https://www.epa.gov/tsca-inventory                                 |
| ECHA CLP Annex VI  | `clp`  | `clean_clp()`  | 9, 10, 13, 14, 15, 17 | https://echa.europa.eu/en/information-on-chemicals/annex-vi-to-clp |
| ECHA EC            | `ec`   | `clean_ec()`   | *Unknown*             | https://echa.europa.eu/information-on-chemicals/ec-inventory       |


## Installation

You can install the development version of cleanventory from 
[GitHub](https://github.com/) with:

```{r install}
#| eval = FALSE

# install.packages("devtools")
remotes::install_github("RaoulWolf/cleanventory")
```

## Examples

This is an example which shows you how to get the data set of the US EPA TSCA:

```{r example}
library(cleanventory)
str(tsca)
```

## Acknowledgement

This R package was developed as part of the project ["ZeroPM: Zero pollution of 
Persistent, Mobile substances"](https://zeropm.eu/). This project has received 
funding from the European Union's Horizon 2020 research and innovation 
programme under grant agreement No 101036756.
